### 2022-04-29 introduction/introduction.tex
teletubbies
more

The proofs need to be spelled out in minute detail to be accepted by a proof assistant.
Even though many proof assistants offer some sort of automation, seemingly simple
statements cannot be automatically proved. This is one of the reasons why large
verification projects can take years to finish.

@@

  First, we implemented the complete superposition calculus for $\lambda$-free
  higher-order logic \cite{bbcw-21-lfho} in E, obtaining a prover we call Ehoh.
  We had to modify the internal term representation of E to support $\lambda$-free
  higher-order terms, implement new unification and matching algorithms, extend
  term indexing data structures to work with higher-order terms, and improve the
  performance of heuristics on higher-order problems.

@@

  We also noticed that Zipperposition's support for first-class Booleans
  was lacking compared to competition. We have closely studied the problems on
  which Zipperposition fails but are easily solved by other provers, and created
  a set of incomplete rules that enhance Zipperposition's Boolean support.
  Zipperposition 2 implemented these rules together with the new unification
  algorithm. In 2020, Zipperposition 2 won the higher-order division
  of CASC \cite{gs-21-cascj10}. This time it was 20 percent points ahead of the second best
  prover, Satallax.

>>>>

The proofs need to be spelled out in minute detail to be accepted by a proof assistant.
Even though many proof assistants offer some sort of automation, seemingly simple
statements cannot be automatically proved. This is one of the reasons why large
verification projects can take years to finish. Thus, providing some level of proof automation
can substantially increase productivity of users of proof assistants.

@@

  First, we implemented the complete superposition calculus for $\lambda$-free
  higher-order logic \cite{bbcw-21-lfho} in E, obtaining a prover we call Ehoh.
  The name of the prover is a word play which combines one of the hit songs by the
  Teletubbies\footnote{\url{https://en.wikipedia.org/wiki/Teletubbies_say_\%22Eh-oh!\%22}}
  and the fact that our prover is a higher-order (HO) extension of E.
  We had to modify the internal term representation of E to support $\lambda$-free
  higher-order terms, implement new unification and matching algorithms, extend
  term indexing data structures to work with higher-order terms, and improve the
  performance of heuristics on higher-order problems.

@@

  \looseness=-1
  We also noticed that Zipperposition's support for first-class Booleans
  was lacking compared to competition. We have closely studied the problems on
  which Zipperposition fails but are solved by other provers, and created
  a set of incomplete rules that enhance Zipperposition's Boolean support.
  Zipperposition 2 implemented these rules together with the new unification
  algorithm. In 2020, Zipperposition 2 won the higher-order division
  of CASC \cite{gs-21-cascj10}. This time it was 20 percent points ahead of the second best
  prover, Satallax.
